Climate control for performant HPUs

### 2014-04-10 docs/draft/draft1.tex
update to manuscript

\section*{Abstract}
\textbf{}
\section*{Introduction}
There are still many tasks for which humans outperform computers
These tend to be tasks that rely on a large repertoire of prior knowledge,
the excercise of common sense judgment, certain visual tasks, and 
tasks that require spontaneous hypothesis generation.

With the emergence of microtask platforms like Amazon Mechanical Turk (AMT),
comes the hope of building compute in which human intelligence can be accessed
on-demand.  This leads to an analogy of the human to the CPU, wherein we think
of human processing units.

A major challenge in building systems that deliver on this vision is the 
natual variability obtained in HPU output.  In some tasks, this variability
is desireable.  For example, in an image labelling task, the natural 
variability in
HPU output leads to greater coverage of the semantic space occupied by an 
image.  In other cases this variability can be problematic, such as in a 
transcription task, where there is only one corect output, and any variability
is only noise.

Whether desired or not, to build up efficient systems from HPUs, one must 
understand the natural variance quantitatively, and understand the factors that
influence it.

Here we model the variance between HPUs as comming from two sources.  The first
is a persistent, or intrinsic variability.  We imagine that this to encompass  
temperamental predispositions, life history, and developmental stage of the 
individual.  While
it may change over the course of a person's lifetime, in the view of the 
computational architect, it is essentially constant.

The seccond is a short-term variability, which arises from the fact that 
peoples immediate state is a function of recent events.  This would include
such things as an HPU becomming more efficient at a task once it has completed
a few tasks of the same type.  It would also include such things as the 
potentially detrimental effects of a noisy environment.

In this view, one can imagine HPUs being different in their specifications,
and also exhibiting hysteresis, whereby their output at some time $t$ is a
function of their inputs at time $t$, $t-1$, and so on.

In psychology, the act of producing these short-lived states that effect a
person's performance during a task is called \textit{priming}.  We will adopt
this term throughout the present work.

\section*{Prior Work}
Priming itself can be broken into many types, and many studies exist exploring
the effects of overt priming on the performance of HPUs. Priming may arise
due to how the task is framed.  This includes such things as the stated
purpose of the task, and the identity of the requester the task.

In \cite{chandler2013breaking}, the researchers investigate the effects of 
framing task either in a meaningful or meaningless way.  Compared to a 
zero-context control treatment, workers increase their output (for less pay),
when they are told that they are helping identify cancer, but there is no
change in quality.  When workers are told that their submissions will be 
discarded, there is no change in the amount of work done, but the quality 
declines.

Another source of priming can be due to what might be called 
\textit{sidestream information}: information that is presented to the 
individual but which is not actually salient to the task.

Other researchers have studied how having peer's responses available to 
the task could influence the worker.

In the present work, we focus on a more subtle source of priming, which arises
simply from the worker's performance in earlier stages of the task.

We compare this to priming arising from framing the task by disclosing a 
(fictitious) funding agency that is paying for the study in which they are 
participating.

\section*{Framework}
At this point we have surveyed some of the conceptual framework traditionally
used to discuss priming in the context of psychology.  Having the origin that
they do, these frameworks are suited to describing the internal mechanisms of
the mind from which they arise.  For our purposes here, we are interested 
primarily in the \textit{effects} of priming, and so it makes sense to 
adopt a position conducive to those ends.  Since our interest in priming 
arises from a desire to construct computing systems from HPUs, we shall
propose a well-defined algorithmic definition for priming.

We must first remark that it does not make sense to speak of an un-primed 
state.  A person can be no more un-primed than a ship at sea can have no 
bearing.  Next, we propose that priming should generally be regarded as a
property of a population of HPUs, rather than as the state of a single HPU.
This is rather like the notion of temperature in thermodynamics.  Although
it does make sense to speak of the kinetic energy of a single molecule, 
Temperature is a statement about the distribution of kinetic energies in a
population of molecules.  The definition of priming which we presently submit
will also be defined in terms of populations.

Two populations, \textsc{j} and \textsc{k} are said to be 
\textit{differently primed} with respect to a task $\mathcal{T}$ if there 
exists a polynomial-time algorithm $\mathcal{A}$ that can distinguish 
(classify) members of \textsc{j} and \textsc{k} with accuracy $\theta$, when 
$\mathcal{A}$ is provided the labelled work-products of HPUs from \textsc{j} 
and \textsc{k} tasked with $\mathcal{T}$.
When $\mathcal{A}$ exists, we say that \textsc{j} and \textsc{k} deviate by 
$\theta$ in priming.

@@

\begin{figure}
	\includegraphics[scale=0.4]{../figs/longitude0.pdf}
	\caption{caption here}
	\label{fig:longitude}
\end{figure}

>>>>

\section*{Abstract}
\textbf{}
\section*{Introduction}
Although capabilities in artificial intelligence continue to advance, 
there are still many tasks for which human performance exceeds that of 
computers now and in the forseable future.  Tasks requiring repertoire of 
general knowledge about the world, the use of common sense or expert judgment, 
finding creative solutions to open-ended questions, and spontaneously 
hypothesis generation outside any apparent framework, are all examples of 
tasks that are routine for humans, but very difficult or impossible for 
computers.  The image labelling task is perhaps the canonical human 
intelligence task (HIT), perhaps because it is simply stated, nearly effortless
for humans, but still extremely challenging for computers.

Rather than replicate human intelligence, there is an alternate vision in 
which human intelligence can be freely accessed and meshed with artificial
intelligenc.  The emergence of microtask platforms like Amazon Mechanical 
Turk (AMT) has made this vision a reality to some extent.  In this paradigm,
the human processing unit (HPU) becomes one component in a hybrid 
computational system, analagous to the CPU.

But there are major challenges in building systems that deliver on this 
vision.  People are far more complex than manufactured chips, 
and so HPU performance is noisy, and subject to bias, leading to uncertain
quality of output.  Of course, the effect that HPU noise has on a compute job 
will depend on the application.
In the image labelling task, some variability is desireable, because it helps
generate sets of labels that in some sense cover semantic space occupied by an 
image.  In other cases this variability can be problematic.  In a 
transcription task, usually there is only one correct output, and so 
variability in the output only degrades quality.

Regardless of the application, the understanding HPU variance quantititively,
and the factors that influence it, will help design of efficient compute 
systems built from HPUs.

Much has been written on the factors that influence human input in 
crowdsourcing platforms.  This has generally related to the context in which
the HPU engages the task.  Unfortunately, especially for platforms like AMT,
this context is out of the designers control, and the relative anonymity of
workers makes it difficult to select for specific conditions.

In the present work, we compare influences that arise from the framing of the
task to influences that arise in-task from the mere act of working.  What 
are the effects of performance that arise simply from how the worker's 
attention is influenced by the previous task, and how do these relate 
quantititively to other pre-task influences?

We pay workers on AMT to label images, and analyze the effects brought about
by subjecting them to different priming treatments, either in the form of 
disclosing a semantically charged name of a (fictitious) organization 
funding the research, or by altering the first few images presented to the
workers.  Surpisingly, simply altering the first few images produces a much
stronger shift in subsequent labelling performance than does disclosing the 
semantically-laden name of the funder.

\section*{Prior Work}

When considering the design of computing systems based on HPUs, we can think
of variability in HPU output as having a relatively persistent component,
and a transient one.  The persistent component would include intrinsic
qualities of a person, such as their temperament, life history, and their 
current developmental stage.  Such characteristics cannot be influenced by
the designer, but it may be possible to screen or at least characterise them 
to some extent.

The transient component of variability might include such factors as influence
alertness, orientation focus, mood, meaningfulness of the task, and any number
of aspects of mental state too subtle to describe.  Such aspects are partly
in the control of the system designer, and can be controlled through how the
task is framed and set up.

In psychology, the phenomenon of priming occurs when a prior stimulus 
makes a person more likely to respond to a task in a particular way.  The 
phenomenon is well-studied, and is believed to follow perceptual, semantic,
or conceptual similarities between the priming stimulus and the ensuing 
response.

Drawing from this insight, it is natural to wonder whether current HPU 
performance might be modulated by recently performed tasks.

Existing work on the effects of human input in crowdsourcing platforms has
generally focused on effects arising from auxilliary information, which has
been added into the task setting, or which frames the task during its 
introduction.

For example, it was shown that framing a task in a meaningful or meaningless
way influences both task quality and the willingness of workers to produce
more output given a declining payment schedule \cite{chandler2013breaking}.
Surprisingly, relative to a zero-context treatment, although workers who were
told that there contributions would be used to help identify cancerous cells
were willing to provide more work, their work was not of a sufficiencly higher
quality.  The only effect on quality occered when workers were told that their
output would be discarded, in which case quality declined.

Another study investigated the influence of providing workers with information
about one another.  This study found that workers were willing to provide
more output, when they were able to see one another's names.  The effect was 
stronger when workers could also see some basic self-reported demographic 
information, and more still when they could see one another's responses.

In the present work, we focus on a perhaps unusual source of priming---that 
arising from the task itself, and compare this to priming that results from 
framing the work as part of study by a named organization.  Given that the 
mechanisms of priming are believed to be related to the residual activation of
perceptual, semantic, and conceptual representations, we hypothesize that 
\textit{in-task} priming could produce effects quantitively comparable to those
produced by framing.

\section*{Theoretical Framework}
Having discussed very briefly some mechanisms and cases of priming, we shall 
now seek to put forward, as an additional testable contribution, a rigorous
definition for priming that is suitable for the study of computing with HPUs.

First, we remark that it does not make sense to speak of an un-primed 
state.  When a person engages in a task, she comes to the task with some 
state of mind.  We therefore do not attempt to define priming in an absolute
sense, but rather, in a relative sense, that is, one priming can be said to 
be different from another.

Also, the effects of a given treatment will depend on the task to which the 
HPUs are put.  In other words, a treatment which generates a strong effect on
the output in one task, does not necessarily produce a strong effect on the
output for other tasks.  On a related note, the study of the effects of priming
on HPUs should be defined algorithmically.  Only effects on HPU output that
can be detected algorithmically can be relevant to a computing system built 
from HPUs.

Further, since only the influence on populations of HPU outputs can be 
meaningfully measured, and since accessing HPU power generally involves 
sampling from a pool of HPU workers, we define priming as a property of a 
population of HPU outputs.  Having said these remarks, we now present an
algorithmic definition of HPU priming:

Two populations of HPU outputs, \textsc{j} and \textsc{k}, are said to be 
\textit{differently primed} with respect to a task $\mathcal{T}$ if there 
exists an algorithm $\mathcal{A}$ which runs in time polynomial in the size
of \textsc{j} and \textsc{k}, that can distinguish 
(classify) members of \textsc{j} and \textsc{k} with accuracy 
$\frac{1+\theta}{2}$, on input \textsc{j} and \textsc{k}.  Further, $\theta$
must be a non-negligible function of $|\textsc{j} + \textsc{k}|$.
If such an $\mathcal{A}$ exists, 
we say that \textsc{j} and \textsc{k} deviate by $\theta$ in priming.

@@

\begin{figure}
	\includegraphics[scale=0.58]{../figs/longitudinalF1scores.pdf}
\caption{$F_1$-score for a naive Bayes classifier trained to distinguish
	HPUs from $\textsc{ingr}_{img}$ and $\textsc{cult}_{img}$ based on 80  
	instances from each treatment, and tested using 20 instances.  Here we
	present the performance of the classifier when only the labels from 
	specific images are presented, to exhibit whether its performance degrades 
	as the number of subtasks since priming increases. 
	}
	\label{fig:longitude}
\end{figure}
